Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-09 Methods.tex
Match up notations, remove occlusions.

\begin{table}
\center
\begin{tabular} {|l | l | c|}
\hline
Name & Description & Value \\ \hline
\(N_{w}\) & Number of women & 1000 \\ \hline
\(N_{m}\) & Number of midwives & 100 \\ \hline
\(R_{m}\) & Number of appointments per midwive & 1000 \\ \hline
\(R_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
Runs & Simulation runs & 1000 \\ \hline
\(P_{h,w}\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
\(P_{m,w}\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
\(P_{l,w}\) & Proportion of light drinkers & \(1/3\) \\ \hline
\(P_{h,m}\) & Proportion of harsh midwives & \(5/100\) \\ \hline
\(P_{m,m}\) & Proportion of moderate midwives & \(10/100\) \\ \hline
\(P_{l,m}\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
\(p_{w}\) & Probability of women sharing & 0. \\ \hline
\(q_{w}\) & Weight of shared information for women & 0. \\ \hline
\(p_{m}\) & Probability of midwives sharing & 0. \\ \hline
\(q_{m}\) & Weight of shared information for midwives & 0. \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 10:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}
\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
In general, we follow the procedure outlined in \cite{Bijak2013b} for stochastic

@@

\begin{table}
\center
\begin{tabular} {|l | l | l| l|}
\hline
Name & Description & Min & Max \\ \hline
\(P_{h,w}\) & Proportion of heavy drinkers & 0 & 1 \\ \hline
\(P_{m,w}\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
\(P_{l,w}\) & Proportion of light drinkers & 0 & 1 \\ \hline
\(P_{h,m}\) & Proportion of harsh midwives & 0 & 1 \\ \hline
\(P_{m,m}\) & Proportion of moderate midwives & 0 & 1 \\ \hline
\(P_{l,m}\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
\(p_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
\(q_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
\(p_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
\(q_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
\(P_{h,}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
\(P_{c, r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(Payoff_{baby} - 1)\)} \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1:1 & 100:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
\end{table}

>>>>

\begin{table}
\center
\begin{tabular} {|l | l | c|}
\hline
Name & Description & Value \\ \hline
\(n_{w}\) & Number of women & 1000 \\ \hline
\(n_{m}\) & Number of midwives & 100 \\ \hline
\(r_{m}\) & Number of appointments per midwive & 1000 \\ \hline
\(r_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
Runs & Simulation runs & 1000 \\ \hline
\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ \hline
\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
\(q_{w}\) & Probability of women sharing & 0. \\ \hline
\(w_{w}\) & Weight of shared information for women & 0. \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0. \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0. \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 10:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}
\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
In general, we follow the procedure outlined in \cite{Bijak2013b} for stochastic

@@

\begin{table}
\center
\begin{tabular} {|l | l | l| l|}
\hline
Name & Description & Min & Max \\ \hline
\(p_{w}(h)\) & Proportion of heavy drinkers & 0 & 1 \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 0 & 1 \\ \hline
\(p_{m}(h)\) & Proportion of harsh midwives & 0 & 1 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 0 & 1 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
\(q_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
\(w_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
\(X_{h,}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
\(X_{c, r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(X_{h} - 1)\)} \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1:1 & 100:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
\end{table}

### 2014-07-09 Model.tex
Match up notations, remove occlusions.

%Might belong in a more methody bit? Read some stuff to check..
Women are drawn in order from a queue, and play against a midwife chosen at random. They play for a maximum of 12 rounds (following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred. At which point a new player is drawn from the same distribution that produced the original players to replace them. If they are not referred, they rejoin the back of the queue after their appointment. In either case, they are informed of their payoff after each round and update their beliefs accordingly.

Midwives play for \(R_{m}\) rounds (\(R_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e. if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives. 
Unlike women, midwives are only informed of their payoff if they choose to make a referral. Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.

Formally then, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\). Additionally define a utility function \(u_{i}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), and distributions over types \(p_{w}(l, m, h), p_{m}(l, m, h)\).

@@

Where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
more than zero and summing to less than 1, and \(\alpha_{i}\) is the integer
psuedo-count of prior observations for a pair \(i\).

@@

Agents then choose $s_{i}$ to minimise $R_{i}$, which is simply - 
\begin{equation}
R_{w}(s_{w}) = \sum_{x\in \Theta} -xp(x | s_{w})
\end{equation}
\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{x\in \Theta} -xp(x | s_{w}\wedge s_{m})
\end{equation}

@@

The second Bayesian agent augments the reasoning of the simple payoff model, making the stronger assumption that the utility function is static, and known. Women maintain two sets of beliefs, one each for \(g\) and \(h\), corresponding respectively to \(p_{m}\), and the probability of referral. This leads to the risk function -

@@

It would seem unreasonable to suppose that neither party recounts their experiences to their peers, and to explore the impact of this we also modify the game to introduce a simple form of information sharing within agent groups. This takes the form of having each agent share their memories with their colleagues with some probability \(p\). Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(q\), and \(0\leq q\leq 1\) (i.e. \(n_{j} = n_{j} + q\)).
Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes. By the same rationale, midwives share only their history with the most recent woman they referred. Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{Memories of games remain, but it is assumed that only current news is relevant.}

>>>>

%Might belong in a more methody bit? Read some stuff to check..
Women are drawn in order from a queue, and play against a midwife chosen at random. They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred. At which point a new player is drawn from the same distribution that produced the original players to replace them. If they are not referred, they rejoin the back of the queue after their appointment. In either case, they are informed of their payoff after each round and update their beliefs accordingly.

Midwives play for \(r_{m}\) rounds (\(r_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e. if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives. 
Unlike women, midwives are only informed of their payoff if they choose to make a referral. Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.

Formally then, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\). Additionally define a utility function \(u_{i}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), and distributions over types \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\).

@@

Where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
more than zero and summing to less than 1, and \(\alpha_{i}\) is the 
psuedo-count of prior observations for a pair \(i\).

@@

Agents then choose $s_{i}$ to minimise $R_{i}$, which is simply - 
\begin{equation}
R_{w}(s_{w}) = \sum_{x \in X} -xp(x | s_{w})
\end{equation}
\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{x \in X} -xp(x | s_{w}\wedge s_{m})
\end{equation}

Where $X$ is set of payoffs the agent has observed to follow $s$.

@@

The second Bayesian agent augments the reasoning of the simple payoff model, making the stronger assumption that the utility function is static, and known. Women maintain two sets of beliefs, corresponding respectively to \(p_{m}\), and the probability of referral given signal choice. This leads to the risk function -

@@

It would seem unreasonable to suppose that neither party recounts their experiences to their peers, and to explore the impact of this we also modify the game to introduce a simple form of information sharing within agent groups. This takes the form of having each agent share their memories with their colleagues with some probability \(q\). Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(w\), and \(0\leq w\leq 1\) (i.e. \(n_{j} = n_{j} + w\)).
Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes. By the same rationale, midwives share only their history with the most recent woman they referred. Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{Memories of games remain, but it is assumed that only current news is relevant.}
